Should I Airbnb My Property?

### 2017-03-09 abb_Writeup.Rmd
Chunk Cosmetics

  stra.rev <- str.data[,c('bedrooms', 'str.ext.revenue')]
  stra.rev$tenure <- 'Short-Term (Actual)   '
  names(stra.rev)[2] <- 'revenue'
  strp.rev <- str.data[,c('bedrooms', 'str.pot.revenue')]
  strp.rev$tenure <- 'Short-Term (potential)   '
  names(strp.rev)[2] <- 'revenue'
  ltr.rev <- ltr.data[,c('bedrooms', 'ltr.revenue')]
  ltr.rev$tenure <- 'Long-Term   '
  names(ltr.rev)[2] <- 'revenue'
  revdens.data <- rbind(stra.rev, strp.rev, ltrrev)

  ggplot(allr, aes(x=revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
    scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
    #ggtitle('Annual Revenues by Tenure Type') +
    xlab('\nAnnual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20k', '$40k', '$60k'))+
    theme(legend.position='none',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000)) +
    facet_wrap(~tenure)

@@

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'}

  str.data.ic$pref <- str.data.ic$str.ext.pref

  rawocc <- abbPrefPlot(str.data.ic,
                         x.field='occ.rate',
                         smooth=TRUE,
                         smooth.span=.5)

  rawocc <- ggplot(rawocc$data,
                   aes(x=x.var, y=Var))+
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='none') + 
    ggtitle('Raw Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

  str.data.ic$occ.qtl <- makeWtdQtl(str.data.ic$occ.rate, 
                                      return.type='rank') 
  str.data.ic$rate.qtl <- makeWtdQtl(str.data.ic$med.rate, 
                                  return.type='rank') 
  qtlocc <- abbPrefPlot(str.data.ic,
                        x.field='occ.qtl',
                        smooth=TRUE,
                        smooth.span=.5)

  qtlocc <- ggplot(qtlocc$data,
                   aes(x=x.var, y=Var))+
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate (Pcntl)') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25th', '50th', '75th', '100th')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='none') + 
    ggtitle('Percentile Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

  ggMultiPlots(rawocc, qtlocc, cols=2)
```

@@

```{r, fig.width=8, fig.height=4, echo=FALSE, fig.align='center', fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'}

@@

@@

@@

```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='\\label{metrohmp}Analysis of Percentile Rates: Metro Level'}

@@

@@

@@

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}

  apt.id <- which(str.data.ic$type == 'Apartment')
  house.id <- which(str.data.ic$type == 'House')
  type.data.ic <- str.data.ic

@@

@@

  type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id],
                                      return.type='rank')
  type.data.ic$occ.qtl[house.id] <- makeWtdQtl(
    type.data.ic$occ.rate[house.id], return.type='rank')

@@

```{r, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}

@@

@@

```{r message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'}

@@

 # Limit to the extrapolated pref type
  pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ]
  pref.table[,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
  pref.table[,2] <- paste0(sprintf('%.1f', pref.table[,2]*100), '%')

  names(pref.table) <- c('Sub-Market', 'Short-Term Preferable')
  options(xtable.comment = FALSE)
  print(xtable(pref.table[,1:2], caption='Geographic Submarket Preferability\n',
               digits=1,
               align='llr'),
               include.rownames=FALSE,
               caption.placement='top')

@@

There is a noticable variability in the relationship between occupancy rates and short-term preference across the submarkets. For raw rates (\autoref{smocc}, left panel), rural properties can acheive short-term preference with lower occupancies than the other areas. This may be due to the relatively low long-term rental rates in the more rural areas coupled with high short-term rates for homes in wine country or near the mountainous terrain east of the city. Transforming to percentiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the others, with suburban and city as the most difficult markets.

```{r, fig.width=8, fig.height=4, echo=FALSE}

  cc.id <- which(str.data.ic$sub.mrkt == 'city-core')
  city.id <- which(str.data.ic$sub.mrkt == 'city')
  sub.id <- which(str.data.ic$sub.mrkt == 'suburban')
  rural.id <- which(str.data.ic$sub.mrkt == 'rural')
  beach.id <- which(str.data.ic$sub.mrkt == 'beach')

@@

  subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id],
                                      return.type='rank')
  subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id],
                                  return.type='rank')

@@

```{r, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Metro Level'}

  sm.col <- abb.col[c(1, 3, 6, 5, 2)] 
  smrocc <- abbPrefPlot(subm.data.ic,
                         x.field='occ.rate',
                         split.field='sub.mrkt',
                         smooth=TRUE,
                         smooth.span=.5 ,
                         spl.col=sm.col)

@@

  ggMultiPlots(smr.occ, smq.occ, cols=2)
```

@@

```{r, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'}

  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
                                          'city-core', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none') +
    ylab('') +
    xlab('') +
  annotate("text", x = 50, y = 50, label = "City-Core", size=9)

@@

```{r, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'}

@@

In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in short-term leasing than apartments. There is very little significant difference between 1 bed / 1 bath units and the remaining categories, with the exception of 2 bed / 2 bath. This could be due to the fact that 2 bed / 2 bath units may be very attractive in the long-term market as they are a useful product for two, non-family roomates to share. Additionally, short-term tenants may not appreciate (pay) for the second bathroom as extra bathrooms are less of amenity during a short vacation stay than in day-to-day living.

Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the City Core (the reference category) when controlling for structural characteristics.  The difference between the Rural and City-Core is not significant, however. The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking the robustness of those estimates. The coefficient for House properties does decrease significantly in magnitude when adding the geographic submarkets.  This is likely due to the fact that houses are concentrated more heavily in City and Suburban areas than in the City-Core and some of the impact of House is being mediated by the geographic submarkets.

@@

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short-Term Preference'}

@@

 makeStatSig <- function(x){
   x <- as.numeric(x)
   y <- rep('***', length(x))
   y[x>.01] <- '** '
   y[x>.05] <- '*  '
   y[x>.1] <- '   '
   y
 }
 m1sig <- makeStatSig(m1[,4])
 m2sig <- makeStatSig(m2[,4])
 m3sig <- makeStatSig(m3[,4])

@@

@@

 full.table <- as.data.frame(cbind(rep('x', length(m1c)), m1c, m2c, m3c))
 names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
 full.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
                          '4 Bed & 2 Bath', 'City (Submarket)',
                          'Suburban (Submarket)', 'Rural (Submarket)', 
                          'Beach (Submarket)', 'Guests per Bedroom', 
                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')

@@

  # Custom function
  logDx <- function(log.model, data, resp.var){

    pred <- prediction(predict(log.model, data, type='response'), resp.var)
    auc <- performance(pred, measure='auc')
    ll <- logLik(log.model)
    AIC <- AIC(log.model)

    return(list(AIC=AIC,
                logLik=ll,
                auc=auc))
  }

@@

@@

 x.full <- xtable(full.table,
                  caption='Logistic Modeling Results\n')
 align(x.full) <- 'lllll'

 print(x.full,
       include.rownames=FALSE,
       hline.after=c(-1,0,15,20,20),
       caption.placement='top')

@@

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short-Term Preference'}

 # Make Basic comparison table
  tpref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                    split.field='type')

  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]
  spref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                    split.field='sub.mrkt')

  spref.table <- spref.table[spref.table$rev.type == 'Potential', ]
  st.table <- rbind(tpref.table, spref.table)
  st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%') 
  names(st.table) <- c('Sub-Market', 'Short-Term Preferable')
  options(xtable.comment = FALSE)
  print(xtable(st.table[,1:2], 
               caption='Potential Revenue Preferability\n',
               digits=1, align='llr'),
               include.rownames=FALSE,
               caption.placement='top',
               hline.after=c(-1, 0, 2, 7, 7))

@@

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE}

@@

@@

@@

@@

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}

@@

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Potential Short-Term Preference'}

@@

@@

@@

@@

@@

  # Create diagnostic table
  pdiag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
                                      'AUC'),
                           Str.Model=c('', '', round(pstr.dx$AIC,0), 
                                       round(pstr.dx$logLik, 0),
                                       round(as.numeric(pstr.dx$auc@y.values),
                                             3)),
                           Sm.Model=c('', '', round(psm.dx$AIC,0), 
                                      round(psm.dx$logLik, 0),
                                      round(as.numeric(psm.dx$auc@y.values),
                                            3)),
                           Host.Model=c('', '', round(phost.dx$AIC,0), 
                                        round(phost.dx$logLik, 0),
                                        round(as.numeric(phost.dx$auc@y.values),
                                              3)))
  names(pdiag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")

@@

@@

 print(px.full,
       include.rownames=FALSE,
       hline.after=c(-1, 0, 15, 20, 20),
       caption.placement='top')

@@

@@

@@

@@

@@

ps.host <- base.host + 
  geom_point(data=str.data[str.data$host.type == 'Profit Seeker', ], size=.4)  +
  ggtitle('Profit Seekers')
os.host <- base.host + 
  geom_point(data=str.data[str.data$host.type == 'Opportunistic Sharer', ], 
             size=.4)  +
  ggtitle('Opportunistic Sharer')
mu.host <- base.host + 
  geom_point(data=str.data[str.data$host.type == 'Multi-Platform User', ], 
             size=.4)  +
  ggtitle('Multi-Platform User')
un.host <- base.host + 
  geom_point(data=str.data[str.data$host.type == 'Unknown', ], size=.4)  +
  ggtitle('Unknown')

@@

@@

```{r results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}

@@

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='\\label{logpot}Logistic Model Results of Potential Short-Term Preference'}

@@

 h1sig <- makeStatSig(h1[,4])
 h2sig <- makeStatSig(h2[,4])
 h3sig <- makeStatSig(h3[,4])

@@

@@

<!-- Heat map with other characteristics on axis

<!-- ### Submarkets -->

<!-- ### Flexible Geo Analysis -->

<!-- ### Logit Models (maybe?) -->

<!-- ### Reference to Shiny App -->

<!-- ## Future Research -->

<!-- - Does time of purchase (which month) matter? -->

<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx'} -->

<!--   host.data.ic <- str.data.ic -->

<!--   ps <- which(str.data.ic$host.type == 'Profit Seeker') -->
<!--   os <- which(str.data.ic$host.type == 'Opportunistic Sharer') -->
<!--   mu <- which(str.data.ic$host.type == 'Multi-Platform User') -->
<!--   un <- which(str.data.ic$host.type == 'Unknown') -->

<!--   host.data.ic$occ.qtl[ps] <- makeWtdQtl( -->
<!--       host.data.ic$occ.rate[ps], return.type='rank') -->
<!--   host.data.ic$rate.qtl[ps] <- makeWtdQtl( -->
<!--     host.data.ic$med.rate[ps], return.type='rank') -->

<!--   host.data.ic$occ.qtl[os] <- makeWtdQtl( -->
<!--       host.data.ic$occ.rate[os], return.type='rank') -->
<!--   host.data.ic$rate.qtl[os] <- makeWtdQtl( -->
<!--     host.data.ic$med.rate[os], return.type='rank') -->

<!--   host.data.ic$occ.qtl[mu] <- makeWtdQtl( -->
<!--       host.data.ic$occ.rate[mu], return.type='rank') -->
<!--   host.data.ic$rate.qtl[mu] <- makeWtdQtl( -->
<!--     host.data.ic$med.rate[mu], return.type='rank') -->

<!--   host.data.ic$occ.qtl[un] <- makeWtdQtl( -->
<!--       host.data.ic$occ.rate[un], return.type='rank') -->
<!--   host.data.ic$rate.qtl[un] <- makeWtdQtl( -->
<!--     host.data.ic$med.rate[un], return.type='rank') -->

<!-- ```     -->

<!-- For the profit-seekers,  -->

<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx55'} -->

<!--   ps.raw.hm.svm <- abbHeatMap(host.data.ic[ps, ], -->
<!--                    x.field='occ.rate', -->
<!--                    y.field='med.rate', -->
<!--                    pref.field='str.ext.pref', -->
<!--                    svm=T, -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=F, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   ps.raw.hm.svm <- ps.raw.hm.svm + ylab('Nightly Rate') -->

<!--   ps.qtl.hm.svm <- abbHeatMap(host.data.ic[ps, ], -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.ext.pref', -->
<!--                    svm=T, -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   ps.qtl.hm.svm <- ps.qtl.hm.svm + ylab('Nightly Rate (Qtl)') -->

<!-- ``` -->

<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx44'} -->

<!-- ggMultiPlots(ps.raw.hm.svm, ps.qtl.hm.svm, cols=2) -->

<!-- ``` -->

<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx33'} -->

<!--   os.raw.hm.svm <- abbHeatMap(host.data.ic[os, ], -->
<!--                    x.field='occ.rate', -->
<!--                    y.field='med.rate', -->
<!--                    pref.field='str.ext.pref', -->
<!--                    svm=T,  -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=F, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   os.raw.hm.svm <- os.raw.hm.svm + ylab('Nightly Rate') -->

<!--   os.qtl.hm.svm <- abbHeatMap(host.data.ic[os, ], -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.ext.pref', -->
<!--                    svm=T,  -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   os.qtl.hm.svm <- os.qtl.hm.svm + ylab('Nightly Rate (Qtl)') -->

<!-- ``` -->

<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx22'} -->

<!-- ggMultiPlots(os.raw.hm.svm, os.qtl.hm.svm, cols=2) -->

<!-- ``` -->

<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of short-term Preference', fig.lp='xxx11'} -->

<!--   mu.raw.hm.svm <- abbHeatMap(host.data.ic[mu, ], -->
<!--                    x.field='occ.rate', -->
<!--                    y.field='med.rate', -->
<!--                    pref.field='str.ext.pref', -->
<!--                    svm=T, -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=F, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   mu.raw.hm.svm <- mu.raw.hm.svm + ylab('Nightly Rate') -->

>>>>

  ggplot(revdens.data, aes(x=revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
    scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
    #ggtitle('Annual Revenues by Tenure Type') +
    xlab('\nAnnual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20k', '$40k', '$60k'))+
    theme(legend.position='none',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000)) +
    facet_wrap(~tenure)

@@

```{r plot_occ_metro, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{occpref}Probability of Short-Term Preference vs Occupancy Rate'}

 ## Make plots

  # Raw
  raw.occ.metro <- ggplot(rawocc.metro$data,
                   aes(x=x.var, y=Var))+
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='none') + 
    ggtitle('Raw Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

  # Quantile
  qtl.occ.metro <- ggplot(qtlocc.metro$data,
                   aes(x=x.var, y=Var))+
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate (Pcntl)') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25th', '50th', '75th', '100th')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='none') + 
    ggtitle('Percentile Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

  # Make Plot
  ggMultiPlots(rawocc, qtlocc, cols=2)

@@

```{r plot_svmr_metro, fig.width=8, fig.height=4, echo=FALSE, warning=FALSE, fig.align='center', fig.cap='\\label{metrohm}Analysis of Raw Rates: Metro Level'}

 ## Create the rate heat map

@@

 ## Create raw SVM heatmap

@@

 ## Plot

@@

```{r plot_svmq_metro, fig.width=8, fig.height=4, echo=FALSE, fig.cap='\\label{metrohmp}Analysis of Percentile Rates: Metro Level'}

 ## Build percentile heatmap

@@

 ## Build percentile SVM

@@

  ## Make Plots

@@

```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}

 ## Create dataset

  type.data.ic <- str.data.ic

  # Id the types
  apt.id <- which(str.data.ic$type == 'Apartment')
  house.id <- which(str.data.ic$type == 'House')

  # Recalculate the percentiles
  type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id],
                                      return.type='rank')
  type.data.ic$occ.qtl[house.id] <- makeWtdQtl(
    type.data.ic$occ.rate[house.id], return.type='rank')

 ## Calc the occ rate numbers

@@

```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}

 ## Build raw plot

@@

 ## Build Percentile Plots

@@

```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}

 ## Make House SVM Heatmap

@@

 ## Make Apartment SVM Heat Map

@@

```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'}

@@

 # Limit to the extrapolated pref type
  pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ]
  pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
  pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%')

 # Fix names  
  names(pref.table) <- c('Sub-Market', 'Short-Term Preferable')
  options(xtable.comment = FALSE)

 ## Make printable table

  print(xtable(pref.table[,1:2], 
               caption='Geographic Submarket Preferability\n',
               digits=1,
               align='llr'),
        include.rownames=FALSE,
        caption.placement='top')

@@

There is a noticable variability in the relationship between occupancy rates and short-term preference across the submarkets. For raw rates (\autoref{smocc}, left panel), rural properties can acheive short-term preference with lower occupancies than the other areas. This may be due to the relatively low long-term rental rates in the more rural areas coupled with high short-term rates for homes in wine country or near the mountainous terrain east of the city. Transforming to percentiles, we see that the city-core properties can reach short-term preference at a much lower occupancy rate than the others, with suburban and city as the most difficult markets.  
```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}

 ## Build data

@@

  # Get IDs
  cc.id <- which(str.data.ic$sub.mrkt == 'city-core')
  city.id <- which(str.data.ic$sub.mrkt == 'city')
  sub.id <- which(str.data.ic$sub.mrkt == 'suburban')
  rural.id <- which(str.data.ic$sub.mrkt == 'rural')
  beach.id <- which(str.data.ic$sub.mrkt == 'beach')

  # Recalc the percentiles
  subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id],
                                      return.type='rank')
  subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id],
                                  return.type='rank')

@@

```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}

 ## Set colors

  sm.col <- abb.col[c(1, 3, 6, 5, 2)]

 ## Create plot data

  smrocc <- abbPrefPlot(subm.data.ic,
                        x.field='occ.rate',
                        split.field='sub.mrkt',
                        smooth=TRUE,
                        smooth.span=.5 ,
                        spl.col=sm.col)

 ## Make plot objects

@@

 ## Plot

  ggMultiPlots(smr.occ, smq.occ, cols=2)

@@

```{r build_svm_geo, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'}

  # Build the SVM Heatmaps

  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$sub.mrkt ==
                                          'city-core', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5])) +
  theme(legend.position='none') +
    ylab('') +
    xlab('') +
  annotate("text", x = 50, y = 50, label = "City-Core", size=9)

@@

```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'}

@@

In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in short-term leasing than apartments. There is very little significant difference between 1 bed / 1 bath units and the remaining categories, with the exception of 2 bed / 2 bath. This could be due to the fact that 2 bed / 2 bath units may be very attractive in the long-term market as they are a useful product for two, non-family roomates to share. Additionally, short-term tenants may not appreciate (pay) for the second bathroom as extra bathrooms are less of amenity during a short vacation stay than in day-to-day living. 
Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the City Core (the reference category) when controlling for structural characteristics.  The difference between the Rural and City-Core is not significant, however. The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking the robustness of those estimates. The coefficient for House properties does decrease significantly in magnitude when adding the geographic submarkets.  This is likely due to the fact that houses are concentrated more heavily in City and Suburban areas than in the City-Core and some of the impact of House is being mediated by the geographic submarkets.

@@

```{r log_model, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short-Term Preference'}

@@

 ## Create vector with significance stars

  m1sig <- makeStatSig(m1[ ,4])
  m2sig <- makeStatSig(m2[ ,4])
  m3sig <- makeStatSig(m3[ ,4])

 ## Create coefficients for the table (with stars)

@@

 ## Even out the lengths

@@

 ##  Create the variable section of table 
 full.table <- as.data.frame(cbind(rep('x', length(m1c)), m1c, m2c, m3c))
 names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
 full.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
                          '4 Bed & 2 Bath', 'City (Submarket)',
                          'Suburban (Submarket)', 'Rural (Submarket)', 
                          'Beach (Submarket)', 'Guests per Bedroom', 
                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')

@@

@@

 ## Combine into full table

@@

  # XTable 
  x.full <- xtable(full.table,
                  caption='Logistic Modeling Results\n')
  align(x.full) <- 'lllll'

  # Print
  print(x.full,
       include.rownames=FALSE,
       hline.after=c(-1,0,15,20,20),
       caption.placement='top')

@@

```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short-Term Preference'}

 # Make Basic comparison table of type
  tpref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                    split.field='type')
 # Extract Potential Results
  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]

 # Make baseic comparison table of submarkets  
  spref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                    split.field='sub.mrkt')

 # Extract potential results  
  spref.table <- spref.table[spref.table$rev.type == 'Potential', ]

 # Combine and round  
  st.table <- rbind(tpref.table, spref.table)
  st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%')

 ## Fix names and print

  names(st.table) <- c('Sub-Market', 'Short-Term Preferable')
  options(xtable.comment = FALSE)
  print(xtable(st.table[,1:2], 
               caption='Potential Revenue Preferability\n',
               digits=1, align='llr'),
               include.rownames=FALSE,
               caption.placement='top',
               hline.after=c(-1, 0, 2, 7, 7))

@@

```{r pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE}

 ## create data and re-estimate the percentiles

@@

 ## Make the pecentile heatmap

@@

 ## Make percentile SVM heatmap

@@

 ## Add annotations to previous SVM

@@

```{r plot_pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}

@@

```{r pot_logmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Potential Short-Term Preference'}

 ## Extract coefficients

@@

 ## Make Significance stars

@@

 ## Create Table coef vectors

@@

 ## Snap to same length

@@

 ## Put together as variables table

@@

  # Create diagnostic table
  pdiag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
                                      'AUC'),
                           Str.Model=c('', '', round(pstr.dx$AIC,0), 
                                       round(pstr.dx$logLik, 0),
                                       round(as.numeric(pstr.dx$auc@y.values),
                                             3)),
                           Sm.Model=c('', '', round(psm.dx$AIC,0), 
                                      round(psm.dx$logLik, 0),
                                      round(as.numeric(psm.dx$auc@y.values),
                                            3)),
                           Host.Model=c('', '', round(phost.dx$AIC,0), 
                                        round(phost.dx$logLik, 0),
                                        round(as.numeric(phost.dx$auc@y.values),
                                              3)))
 ## Fix names

  names(pdiag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")

 # Bind together

@@

 # XTable

@@

 # Print
 print(px.full,
       include.rownames=FALSE,
       hline.after=c(-1, 0, 15, 20, 20),
       caption.placement='top')

@@

  ## Create table of host block frequencies

@@

 ## Create scatter of block rate vs block periods

@@

 ## Split Hosts into groups

@@

  # Create a background plot for the host location plots

@@

  ## Create individual host location plots

  ps.host <- base.host + 
    geom_point(data=str.data[str.data$host.type == 'Profit Seeker', ], size=.4)  +
    ggtitle('Profit Seekers')

  os.host <- base.host + 
    geom_point(data=str.data[str.data$host.type == 'Opportunistic Sharer', ], 
               size=.4)  +
    ggtitle('Opportunistic Sharer')

  mu.host <- base.host + 
    geom_point(data=str.data[str.data$host.type == 'Multi-Platform User', ], 
               size=.4)  +
    ggtitle('Multi-Platform User')

  un.host <- base.host + 
    geom_point(data=str.data[str.data$host.type == 'Unknown', ], size=.4)  +
    ggtitle('Unknown')

@@

 ## Build plot

@@

```{r host_table, results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}

@@

```{r host_logmodel, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='\\label{logpot}Logistic Model Results of Potential Short-Term Preference'}

 ## Extract coefficients

@@

 ## Build significance stars

   h1sig <- makeStatSig(h1[ ,4])
   h2sig <- makeStatSig(h2[ ,4])
   h3sig <- makeStatSig(h3[ ,4])

 ## Create Table coefficients

@@

 ## Convert to variable table

@@
